Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks

### 2020-03-05 paper/eccv2020submission.tex
Doing some good work on the paper

@@

\section{Methodology}\label{methodology}

\emph{The models were trained with real simulation data. We first describe the process of generating said data, then we give details on the training procedure and the architecture of the models. We then descibe the three types of models that we build and evaluated.}

\subsection{Simulation Setup}
The training data was generated by performing numerous simulations of an incompressible fluid flow around a rectangular object in a channel. The simulations were modeled according to the Navier-Stokes equations for incompressible flow. Because we are interested in the image representations of the simulations, we are dealing only with the 2D case. There are several boundary conditions that describe the simulation setup:
\begin{itemize}
\item Inflow condition on the left side of the channel
\item Outflow condition on the right side of the channel
\item No slip condition on bottom and top side of the channel as well as the sides of the object.
\end{itemize}
The simulation setup has three separate adjustable parameters --- inflow speed, fluid density and fluid viscosity.
\\
We generated three sets of simulations for training the three kinds of models.
\begin{itemize}
\item plain: a single simulation with \ldots.
\item varying inflow speed: \ldots simulations with different inflow speed. The inflow speeds are in the range of \ldots with a step of \ldots.
\item varying viscosity and density of the fluid: \ldots simulations all with different fluid viscosity and density. The viscosity was in the range of \ldots with a step of \ldots and the density was in the range of \ldots with a step of \ldots. We used the product of the two parameter ranges to perform simulations with all of the possible combinations between the two parameters.
\end{itemize}

@@

The simulations were performed numerically by solving the differential equation describing the flow --- the Navier-Stokes equation. This was done with a numerical solver --- HiFlow ---  that works on base of Finite element method. The solver supports parallelization with MPI and OpenMP and we used 12 MPI processes to run each simulation. For all of the simulations the timestep for of solver was set to $0.035$ seconds. This means the a single timestep of the simulations corresponds to a $0.035$ seconds of physical time.

The numerical solver on itself cannot be used to render the simulation results to images. For this reason we used ParaView to load the simulation data and exported it as a sequence of images in PNG format. We opted out for using grayscale images as early experiments with RGB-images did not deliver satisfying results. We used the default ``Grayscale'' color preset of ParaView to visualize the results.

\subsection{Network Details}
\emph{In this subsection we turn our attention to the details around the architecture of the used network.}

The architecture of the used network and the training approach are entirely based on pix2pix.

>>>>

Our contributions are \ldots.

@@

\section{Methodology}\label{methodology}
% \emph{The models were trained with real simulation data. We first describe the process of generating said data, then we give details on the training procedure and the architecture of the models. We then descibe the three types of models that we build and evaluated.}

The task is to build a network that can predict the next frame of the simulation based on the previous one. Each frame represents a timestep of the simulation and consists of a three channel image. Two of the channels encode the velocity fields in both directions and the third channel is the pressure field of the fluid. We were interested in how the usage of the pressure field affects the performance of the built models. Therefore, for each model be trained two variants --- one that uses the pressure field and one that does not.

We did not construct a single holistic model that can handle all of the simulation's parameters. Our efforts were concentrated on building a couple of smaller ones that take into account subsets of the parameters. The studied models are:
\begin{itemize}
\item A Constant model --- does not take into any of the parameters and it is trained with data from a single simulation. It is conceived as a baseline and proof of concept model that is there to show how a neural network can learn to generate simulation timesteps in from of images.
\item A fluid inflow speed model --- the model receives the inflow speed of the fluid as an extra input. It is trained with data from several simulations with different inflow speeds.
\item A viscosity and density model --- the model receives the viscosity and density of the fluid as extra inputs.
\end{itemize}
By evaluating each models we want to see how a network can generalize each of the parameter subsets and to what extent

To study the performance of conditional GANs on generating frames of the concrete simulation we generated the training data ourselves. In what follows we give details about the process.

\subsection{Simulation Setup and Data generation}
The training data was generated by performing numerous simulations of an incompressible fluid flow around a rectangular object in a channel. The simulations were modeled according to the Navier-Stokes equations for incompressible flow. Because we are interested in the image representations of the simulations, we are dealing only with the 2D case. There are several boundary conditions that describe the simulation setup:
\begin{itemize}
\item Inflow condition on the left side of the channel
\item Outflow condition on the right side of the channel
\item No slip condition on bottom and top side of the channel as well as the sides of the object.
\end{itemize}
The simulation setup has three separate adjustable parameters --- inflow speed, fluid density and fluid viscosity.
\\
We generated three sets of simulations for training the three kinds of models.
\begin{itemize}
\item plain: a single simulation with \ldots.
\item varying inflow speed: \ldots simulations with different inflow speed. The inflow speeds are in the range of \ldots with a step of \ldots.
\item varying viscosity and density of the fluid: \ldots simulations all with different fluid viscosity and density. The viscosity was in the range of \ldots with a step of \ldots and the density was in the range of \ldots with a step of \ldots. We used the product of the two parameter ranges to perform simulations with all of the possible combinations between the two parameters.
\end{itemize}

@@

The simulations were performed numerically by solving the differential equation describing the flow --- the Navier-Stokes equation. This was done with a numerical solver library --- HiFlow ---  that works on the base of Finite element method. The solver supports parallelization with MPI and OpenMP and we used 12 MPI processes to run each simulation. For all of the simulations the timestep for of solver was set to $0.035$ seconds. This means the a single timestep of the simulations corresponds to a $0.035$ seconds of physical time.

The numerical solver on itself cannot be used to render the simulation results to images. For this reason we used ParaView to load the simulation data and exported it as a sequence of images in PNG format. We opted out for using grayscale images as early experiments with RGB-images did not deliver satisfying results. We used the default ``Grayscale'' color preset of ParaView to visualize the results. Each frame of the simulation was exported as three separate grayscale images. The images were finally cropped to select a subset of the space that contains the object and the space behind it.

\subsection{Training approach and networks details}
\emph{In this subsection we turn our attention to the details around the architecture of the used network.}

We base our generative models almost entirely on pix2pix. We use the conditional GAN approach to train a generator network that can perform image-to-image translation. As explained in [], the traditional GAN method uses a random vector $z$ as in input to the generator network $G$ to generate output $y$, $G:z \rightarrow y$. Conditional GANs also feed an input image $x$ to the generator, $G: x,z \rightarrow y$. Pix2Pix suggests that in certain cases the usage of $z$ can be usefully but we decided not to include for out generator as we want a deterministic network.

We adopt the objective for the discriminator network as we modify it slightly by leaving out the random vector $z$.
\begin{equation}
\mathcal{L}_{cGAN} (G, D) = (\mathbb{E}[\log D (x,y)] + \mathbb{E}[\log D (x, G(x))])/2
\end{equation}
where $x$ is the input image and $y$ is the target image. In contrast to unconditional GANs, both the generator and the discriminator network have access to the input image. The objective is divided by 2 to slow down the training of the discriminator relative to the generator as suggested by [].

The objective for the generator network is comprised of two parts --- the value of the discriminator as well as

% In contrast to pix2pix we also disable the dropout and batch normalization layers during testing.

% Our task is an image generation task we used the conditional GAN method introduced in pix2pix.

% Some of the experiments in pix2pix suggest that keeping the noise vector can be reasonable but we decided to use only a single multichannel image as an input for the generator network.

% The generator is trained to produced the next frame of the simulation based on the previous one. A single frame contains the two velocity fields as well as optional pressure field. We experimented with using and leaving out the pressure field.

% Some of the models, however, also take some simulation parameters into account. For those models, the generator also receives one or two constant channels with a value equal to the value of the parameter.

% The training approach is almost entirely based on pix2pix. We used the conditional GAN (Generative adversarial network) method to build a minimal image translation framework. In contrast to classical GANs, conditional GANs present both the original and the generated image to the discriminator network. The discriminator network is also used as part of the loss function for the generator network.

% In our case, the generator network is presented a single timestep of the simulation in an image form. For the inflow-speed and fluid viscosity-density models the corresponding parameters of the simulation are also given to the network. The parameters are represented as separate constant channels with a value equal to the one of the parameter.
